Foreign direct investment, corporate social responsibility, and malaria control in Mozambique - trends, risks, and opportunities

### 2020-04-18 paper.Rmd
updated

if('search_results.RData' %in% dir()){
  load('search_results.RData')
} else {
  csr_results <- pubmed(start_year = 2000,
                         end_year = 2016,
                         search_topic = '(malaria) and (corporate social responsibility)',
                         counts_only = FALSE,
                         n_records = 5000)  
  fdi_results <- pubmed(start_year = 2000,
                       end_year = 2016,
                       search_topic = '(malaria) and (foreign direct investment)',
                       counts_only = FALSE,
                       n_records = 5000)  
    moz_csr_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (corporate social responsibility)',
                     counts_only = FALSE,
                     n_records = 5000)  
  moz_fdi_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (foreign direct investment)',
                     counts_only = FALSE,
                     n_records = 5000)  
  save(csr_results,
       fdi_results,
       moz_csr_results,
       moz_fdi_results,
       file = 'search_results.RData')
}
pubmed_results <- rbind(csr_results$results %>% mutate(type = 'CSR'),
                        fdi_results$results %>% mutate(type = 'FDI'),
                        moz_csr_results$results %>% mutate(type = 'CSR MOZ'))

@@

```{r}
# Define function for reading fdi data from imf
if('imf.RData' %in% dir()){
  load('imf.RData')
} else {
  read_imf <- function(file){
  srcs <- readxl::read_excel(file, skip = 4)
  # Rename columns
  srcs <- srcs[,1:3]
  srcs <- srcs[2:nrow(srcs),]
  names(srcs) <- c('from_country', 'inward', 'outward')
  # Make numberic
  srcs <- data.frame(srcs)
  for (j in 2:3){
    this_column <- as.numeric(as.character(gsub('.', '', srcs[,j], fixed = TRUE)))
    srcs[,j] <- this_column
  }
  srcs <- srcs %>%
    filter(from_country != 'World')

@@

```{r}
last_year <- x %>%
  filter(year == 2015)
last_year <- last_year %>% 
  arrange(desc(inward)) %>%
  mutate(from_country = factor(from_country, levels = as.character(from_country)))
last_year <- last_year[1:10,]
ggplot(data = last_year,
       aes(x = from_country,
           y = inward)) +
  geom_bar(stat = 'identity',
           alpha = 0.6,
           fill = 'darkblue') +
  labs(x = 'Source of investment',
       y = '2015 USD, Millions',
       title = 'Sources of FDI in Mozambique',
       subtitle = 'By investor country') +
  theme_bw() +
    theme(axis.text.x = element_text(angle = 90)) 
```

@@

                         'FDI MOZ',

@@

econ_results[2,2:5] <- c(2000, 'Administrative barriers to foreign investment: Reducing red tape in Africa', 'FDI MOZ', 'Emery')

@@

                         'FDI MOZ', 'Tembe')

@@

                         'FDI MOZ', 'German')

@@

                         'FDI MOZ', 'Grande')

@@

                         'FDI MOZ', 'Winkler')

@@

                         'FDI MOZ', 'Morisset')

@@

                         'FDI MOZ', 'Bassu')

@@

                         'FDI MOZ', 'Castel-Branco')

@@

                          'FDI Malaria',

@@

# Make short funtion
make_short <- function(x, n = 20){
  if(nchar(x) < n){
    return(x)
  } else {
  return(paste0(substr(x, 1, n), '...', collapse = ''))
  }
}
for (s in 1:nrow(search_results)){
  search_results$Title[s] <- 
    make_short(search_results$Title[s])
    # add_n(search_results$Title[s], n = 60)
}
search_results$Year <- as.character(search_results$Year)
search_results <- search_results %>% arrange(Source, Type)
```

```{r, results = 'asis'}
# kable(search_results)
options(xtable.comment = FALSE)
print(xtable(search_results),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      include.rownames = FALSE,
      include.colnames = TRUE,
      caption.placement = "top",
      comment=FALSE,
      floating=FALSE,
      tabular.environment='longtable')
```

>>>>

if('search_results.RData' %in% dir()){
  load('search_results.RData')
} else {
  csr_results <- pubmed(start_year = 2000,
                         end_year = 2016,
                         search_topic = '(malaria) and (corporate social responsibility)',
                         counts_only = FALSE,
                         n_records = 5000)  
  fdi_results <- pubmed(start_year = 2000,
                       end_year = 2016,
                       search_topic = '(malaria) and (foreign direct investment)',
                       counts_only = FALSE,
                       n_records = 5000)  
    moz_csr_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (corporate social responsibility)',
                     counts_only = FALSE,
                     n_records = 5000)  
  moz_fdi_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (foreign direct investment)',
                     counts_only = FALSE,
                     n_records = 5000)  
  save(csr_results,
       fdi_results,
       moz_csr_results,
       moz_fdi_results,
       file = 'search_results.RData')
}
pubmed_results <- bind_rows(csr_results$results %>% mutate(type = 'CSR | Malaria'),
                        fdi_results$results %>% mutate(type = 'FDI | Malaria'),
                        moz_csr_results$results %>% mutate(type = 'CSR | Mozambique'))

@@

```{r}
# Define function for reading fdi data from imf
if('imf.RData' %in% dir()){
  load('imf.RData')
} else {
  read_imf <- function(file){
  srcs <- readxl::read_excel(file, skip = 5)
  # Rename columns
  srcs <- srcs[,1:3]
  # srcs <- srcs[2:nrow(srcs),]
  names(srcs) <- c('from_country', 'inward', 'outward')
  # Make numberic
  srcs <- data.frame(srcs)
  for (j in 2:3){
    # this_column <- as.numeric(as.character(gsub('.', '', srcs[,j], fixed = TRUE)))
    this_column <- as.numeric(as.character(srcs[,j]))
    this_column <- ifelse(is.na(this_column), 0, this_column)
    srcs[,j] <- this_column
  }
  srcs <- srcs %>%
    filter(from_country != 'World')

@@

```{r}
last_year <- x %>%
  filter(year == 2015)
last_year <- last_year %>% 
  arrange(desc(inward)) %>%
  mutate(from_country = factor(from_country, levels = as.character(from_country)))
last_year <- last_year[1:20,]
ggplot(data = last_year,
       aes(x = from_country,
           y = inward )) +
  geom_bar(stat = 'identity',
           alpha = 0.6,
           fill = 'darkblue') +
  labs(x = 'Source of investment',
       y = '2015 USD, Millions',
       title = 'Sources of FDI in Mozambique',
       subtitle = 'By investor country') +
  theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

@@

                         'FDI | Mozambique',

@@

econ_results[2,2:5] <- c(2000, 'Administrative barriers to foreign investment: Reducing red tape in Africa', 'FDI | Mozambique', 'Emery')

@@

                         'FDI | Mozambique', 'Tembe')

@@

                         'FDI | Mozambique', 'German')

@@

                         'FDI | Mozambique', 'Grande')

@@

                         'FDI | Mozambique', 'Winkler')

@@

                         'FDI | Mozambique', 'Morisset')

@@

                         'FDI | Mozambique', 'Bassu')

@@

                         'FDI | Mozambique', 'Castel-Branco')

@@

                          'FDI | Malaria',

@@

# Make short funtion
make_short <- function(x, n = 20){
  if(nchar(x) < n){
    return(x)
  } else {
  return(paste0(substr(x, 1, n), '...', collapse = ''))
  }
}
for (s in 1:nrow(search_results)){
  search_results$Title[s] <- 
    make_short(search_results$Title[s])
    # add_n(search_results$Title[s], n = 60)
}
search_results$Year <- as.character(search_results$Year)
search_results <- search_results %>% arrange(Source, Type) %>% filter(!duplicated(Title))
```

```{r, results = 'asis'}
# kable(search_results)
options(xtable.comment = FALSE)
print(xtable(search_results),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      include.rownames = FALSE,
      include.colnames = TRUE,
      caption.placement = "top",
      comment=FALSE,
      floating=FALSE,
      tabular.environment='longtable')
# save(search_results, file = 'sr.RData')
```

### 2020-04-18 paper_word.Rmd
updated

if('search_results.RData' %in% dir()){
  load('search_results.RData')
} else {
  csr_results <- pubmed(start_year = 2000,
                         end_year = 2016,
                         search_topic = '(malaria) and (corporate social responsibility)',
                         counts_only = FALSE,
                         n_records = 5000)  
  fdi_results <- pubmed(start_year = 2000,
                       end_year = 2016,
                       search_topic = '(malaria) and (foreign direct investment)',
                       counts_only = FALSE,
                       n_records = 5000)  
    moz_csr_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (corporate social responsibility)',
                     counts_only = FALSE,
                     n_records = 5000)  
  moz_fdi_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (foreign direct investment)',
                     counts_only = FALSE,
                     n_records = 5000)  
  save(csr_results,
       fdi_results,
       moz_csr_results,
       moz_fdi_results,
       file = 'search_results.RData')
}
pubmed_results <- rbind(csr_results$results %>% mutate(type = 'CSR'),
                        fdi_results$results %>% mutate(type = 'FDI'),
                        moz_csr_results$results %>% mutate(type = 'CSR MOZ'))

>>>>

if('search_results.RData' %in% dir()){
  load('search_results.RData')
} else {
  csr_results <- pubmed(start_year = 2000,
                         end_year = 2016,
                         search_topic = '(malaria) and (corporate social responsibility)',
                         counts_only = FALSE,
                         n_records = 5000)  
  fdi_results <- pubmed(start_year = 2000,
                       end_year = 2016,
                       search_topic = '(malaria) and (foreign direct investment)',
                       counts_only = FALSE,
                       n_records = 5000)  
    moz_csr_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (corporate social responsibility)',
                     counts_only = FALSE,
                     n_records = 5000)  
  moz_fdi_results <- pubmed(start_year = 2000,
                     end_year = 2016,
                     search_topic = '(mozambique) and (foreign direct investment)',
                     counts_only = FALSE,
                     n_records = 5000)  
  save(csr_results,
       fdi_results,
       moz_csr_results,
       moz_fdi_results,
       file = 'search_results.RData')
}
pubmed_results <- bind_rows(csr_results$results %>% mutate(type = 'CSR'),
                        fdi_results$results %>% mutate(type = 'FDI'),
                        moz_csr_results$results %>% mutate(type = 'CSR MOZ'))
